### 2013-03-25 doc/dissertation/document/chapters/mc_background/mc_background.tex
changed jacobi to point jacobi in mc background

\subsection{Preconditioning MCSA}
\label{sec:stochastic_preconditioning}
In most cases, at least a minimal amount of \textit{preconditioning}
of the linear system will be required in order to use the class of
stochastic methods described. Although these methods have no symmetry
requirements for convergence, they do require that the spectral radius
of the iteration matrix be less than one. To achieve this for
diagonally dominant matrices, a Jacobi preconditioner, a form of left
preconditioning, is used such that the preconditioning matrix $\ve{M}$
is:
\begin{equation}
  \ve{M} = diag(\ve{A})\:,
  \label{eq:jacobi_preconditioner}
\end{equation}
such that its application means we are instead solving the following
linear system:
\begin{equation}
  \ve{M}^{-1}\ve{A}\ve{x} = \ve{M}^{-1}\ve{b}\:.
  \label{eq:jacobi_precond_linear_problem}
\end{equation}
Next, we can apply MCSA to solve
Eq~(\ref{eq:jacobi_precond_linear_problem}): 
\begin{subequations}
  \begin{gather}
    \ve{x}^{k+1/2} = \ve{x}^k +
    \ve{M}^{-1}\ve{r}^k\:,\\ \ve{r}^{k+1/2} =
    \ve{b}-\ve{A}\ve{x}^{k+1/2}\:,\\ \ve{M}^{-1}\ve{A}\delta\ve{x}^{k+1/2}
    = \ve{M}^{-1}\ve{r}^{k+1/2}\:,\\ \ve{x}^{k+1} = \ve{x}^{k+1/2} +
    \delta \ve{x}^{k+1/2}\:.
    \label{eq:jacobi_preconditioned_mcsa}
  \end{gather}
\end{subequations}
Choosing Jacobi preconditioning with MCSA is advantageous for several
reasons. First, $\rho(\ve{I} - \ve{M}^{-1}\ve{A}) < 1$ is true for all
$\ve{A}$ that is diagonally dominant and is easy to formulate because
the inversion of $\ve{M}$ is trivial. Second, because the adjoint
Monte Carlo method used within MCSA to compute the correction operates
on a linear problem with the preconditioned operator, then $\ve{H}$ in
the adjoint solver will have a zero term in each of its diagonal
elements, thereby eliminating all in-state transitions during the
random walk sequence. Because of this, Jacobi preconditioning should
always be performed, regardless of any other preconditioning that is
applied to the system.

>>>>

\subsection{Preconditioning MCSA}
\label{sec:stochastic_preconditioning}
In most cases, at least a minimal amount of \textit{preconditioning}
of the linear system will be required in order to use the class of
stochastic methods described. Although these methods have no symmetry
requirements for convergence, they do require that the spectral radius
of the iteration matrix be less than one. To achieve this for
diagonally dominant matrices, a point Jacobi preconditioner, a form of left
preconditioning, is used such that the preconditioning matrix $\ve{M}$
is:
\begin{equation}
  \ve{M} = diag(\ve{A})\:,
  \label{eq:jacobi_preconditioner}
\end{equation}
such that its application means we are instead solving the following
linear system:
\begin{equation}
  \ve{M}^{-1}\ve{A}\ve{x} = \ve{M}^{-1}\ve{b}\:.
  \label{eq:jacobi_precond_linear_problem}
\end{equation}
Next, we can apply MCSA to solve
Eq~(\ref{eq:jacobi_precond_linear_problem}): 
\begin{subequations}
  \begin{gather}
    \ve{x}^{k+1/2} = \ve{x}^k +
    \ve{M}^{-1}\ve{r}^k\:,\\ \ve{r}^{k+1/2} =
    \ve{b}-\ve{A}\ve{x}^{k+1/2}\:,\\ \ve{M}^{-1}\ve{A}\delta\ve{x}^{k+1/2}
    = \ve{M}^{-1}\ve{r}^{k+1/2}\:,\\ \ve{x}^{k+1} = \ve{x}^{k+1/2} +
    \delta \ve{x}^{k+1/2}\:.
    \label{eq:jacobi_preconditioned_mcsa}
  \end{gather}
\end{subequations}
Choosing point Jacobi preconditioning with MCSA is advantageous for
several reasons. First, $\rho(\ve{I} - \ve{M}^{-1}\ve{A}) < 1$ is true
for all $\ve{A}$ that is diagonally dominant and is easy to formulate
because the inversion of $\ve{M}$ is trivial. Second, because the
adjoint Monte Carlo method used within MCSA to compute the correction
operates on a linear problem with the preconditioned operator, then
$\ve{H}$ in the adjoint solver will have a zero term in each of its
diagonal elements, thereby eliminating all in-state transitions during
the random walk sequence. Because of this, point Jacobi
preconditioning should almost always be performed, regardless of any
other preconditioning that is applied to the system.
